---
title: "Data Summary for Single DRT task"
author: '[Spencer Castro](http://spencercastro.com)'
date: "2/6/2017"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    fig_height: 4
    highlight: pygments
    theme: yeti
    toc: yes
    toc_float: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center', warning = FALSE, 
                      message = FALSE, results = 'hide', fig.path = "images/")
require(lubridate)
require(tidyverse)
require(RColorBrewer)
require(car)
setwd("~/Documents/R_data/MitchHonors")

rm(list=ls()) #Clear wd()
source("Load_Data.R") #Load the functions
load(file = "CleanData.Rdata") #Load the data
```

#DRT Simple Task

1.a This is a plot for the accuracy of the visual search task (The proportion of trials in which a target was selected compared to a distractor.)

```{r Visual Search Task Accuracy, results='show'}
###Colors for plots
####Create a custom color scale
myColors <- c("forestgreen","grey50")
names(myColors) <- levels(clean$targcol)
colScale <- scale_colour_manual(name = "targcol",values = myColors)

acc.mean <- cleanac %>%
  group_by(condition, targcol) %>%
  summarise(perc_corr = mean(corr)*100)


datac <- summarySEwithin(cleanac, measurevar ="corr", withinvars = c("condition","targcol"), idvar = "subid")

accplot <- ggplot(datac, aes(x = condition, y=corr, color = targcol, group = targcol)) +
  geom_point() + theme_minimal() + geom_point() +
  my.axis.font + geom_errorbar(width = .25,
                               aes(ymin=corr-ci, ymax=corr+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(.95, 1.1)) +
  scale_fill_manual(values=myColors) + ylab("Percent Correct (%)") +
  ggtitle("Accuracy of the \n Visual Search Task \n by Condition")
accplot

vis.ac <- lmer(corr~condition*targcol+(1|subid),data=cleanac)
Anova(vis.ac)

```

The ANOVA here shows that the conditions of blocked and mixed difficulties impacted the accuracy. The difficulty of the target task itself also effected accuracy. However, there was no target color by condition interaction. Almost all groups were at ceiling for accuracy, meaning very few errors were produced, and the effect is very small.

 condition | target color | percent correct |  ci
 ----------|---------|------|------------
     green |  green  |0.9953|  0.0018
     mixed |  green  |0.9993|  0.0010
     mixed |  white  |0.9948|  0.0027
     white |  white  |0.9935|  0.0021


```{r Visual Search Task Reaction Time, results="show"}

datrt <- summarySEwithin(clean, measurevar ="rt1", withinvars = c("condition","targcol"), idvar = "subid")

rtplot <- ggplot(datrt, aes(x = condition, y=rt1, fill = targcol)) +
  geom_bar(stat = "identity", position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(position=position_dodge(.9), width = .25,
                               aes(ymin=rt1-ci, ymax=rt1+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(1000, 3000)) +
  scale_fill_manual(values=myColors) + ylab("Reaction Time (ms)") +
  ggtitle("Reaction Times of the \n Visual Search Task \n by Condition")
rtplot

vis.ac <- lmer(rt1~condition*targcol*corr+(1|subid),data=clean)
Anova(vis.ac)
```
Reaction time was affected by whether the targets were blocked or mixed (condition), the target color was different, or whether the answer was correct or not. There were no interaction effects.

### combined steering with drt
```{r drt and steering, results="show"}
drt.clean$condition <- recode_factor(drt.clean$condition, 
                                     "1" = "practice","2" = "green","3" ="white", "4" = "mixed",
                                     .default = "NA")
drt.clean$response <- recode_factor(drt.clean$response, "1" = "correct", "-1" = "incorrect")

drtrt <- summarySEwithin(drt.clean, measurevar ="rt", withinvars = c("condition","response"), idvar = "subid")

drtrt <- drtrt %>% filter(condition != "practice")

rtplot <- ggplot(drtrt, aes(x = condition, y=rt, fill = response)) +
  geom_bar(stat = "identity", position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(position=position_dodge(.9), width = .25,
                               aes(ymin=rt-ci, ymax=rt+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(200, 700)) + ylab("Reaction Time (ms)") +
  ggtitle("Reaction Times of the \n DRT \n by Condition and Response")
rtplot

drt.rt <- lmer(rt~condition*response*mean.dev+(1|subid),data=drt.clean)
Anova(drt.rt)

```

condition| response |rt      |    ci
 ------|----------|----------|----------
 green |  correct | 567.1133 | 10.026026
 green |incorrect |  546.7265|  31.821575
 mixed |  correct | 573.4649 |  9.423457
 mixed |incorrect | 541.2416 |  32.182574
 white | correct  |589.9847  |  9.402508
 white |incorrect | 517.4245 |  33.214033

Incorrect responses (where the participant responded to the light more than once) were faster on average than correct responses. The difficulty also affected reaction times. In addition, there was a difficulty (condition) by steering deviation interaction. We can see the effect of difficulty on steering below.

```{r drt and steering 2}

drtrt <- summarySEwithin(drt.clean, measurevar ="mean.dev", withinvars = c("condition"), idvar = "subid")

drtrt <- drtrt %>% filter(condition != "practice")

rtplot <- ggplot(drtrt, aes(x = condition, y=mean.dev)) +
  geom_bar(stat = "identity", position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(position=position_dodge(.9), width = .25,
                               aes(ymin=mean.dev-ci, ymax=mean.dev+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(0, 10)) + ylab("Degrees Deviation") +
  ggtitle("Mean Steering Deviation")
rtplot

drt.rt <- lmer(mean.dev~condition+(1|subid),data=drt.clean)
Anova(drt.rt)
```

condition| mean.dev|ci
---------|---------|-----
green | 5.687147 | 0.059
mixed | 7.083614 | 0.137
white | 6.167213 | 0.057

Alone, the effects of the difficulty of the visual task changed the steering deviation so that (1) at the easiest difficulty, steering was best (2) at the highest difficulty, steering was slightly worse, but (3) when participants didn't know whether to expect easy or difficult trials, steering was the worst. Interestingly, the DRT was not sensitive to this phenomenon.


#DRT Choice Task Data

```{r setup2, include=FALSE}

rm(list=ls()) #Clear wd()
source("Load_Data.R") #Load the functions
load("~/Documents/R_data/MitchHonors/MitchChoice/cleanchoiceData.Rdata")
drt.clean.choice <- drt.clean.choice %>%
  dplyr::filter(subid != "03")
```

1.a This is a plot for the accuracy of the visual search task (The proportion of trials in which a target was selected compared to a distractor.)

```{r Visual Search Task Choice Accuracy, results='show'}
###Colors for plots
####Create a custom color scale
myColors <- c("forestgreen","grey50")
names(myColors) <- levels(clean.choice$targcol)
colScale <- scale_colour_manual(name = "targcol",values = myColors)
clean.choice <- clean.choice %>%
  dplyr::filter(subid != "01", subid != "02", subid != "03")
clean.choiceac <- clean.choiceac %>%
  dplyr::filter(subid != "01", subid != "02", subid != "03")

acc.mean <- clean.choiceac %>%
  group_by(condition, targcol) %>%
  summarise(perc_corr = mean(corr)*100)


datac <- summarySEwithin(clean.choiceac, measurevar ="corr", withinvars = c("condition","targcol"), idvar = "subid")

accplot <- ggplot(datac, aes(x = condition, y=corr, fill = targcol)) +
  geom_bar(stat = "identity", position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(position=position_dodge(.9), width = .25,
                               aes(ymin=corr-ci, ymax=corr+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(.9, 1)) +
  scale_fill_manual(values=myColors) + ylab("Percent Correct (%)") +
  ggtitle("Accuracy of the \n Visual Search Task \n by Condition")
accplot

vis.ac <- lmer(corr~condition*targcol+(1|subid),data=clean.choiceac)
Anova(vis.ac)
```

The ANOVA here shows that the conditions of blocked and mixed difficulties did not impact the accuracy. We have a significant effect of the target color, and it didn't matter whether the targets were blocked or mixed.

 condition | target color | percent correct |  ci
 ----------|---------|------|------------
     green |  green  |0.9932|  0.0030
     mixed |  green  |1.0000|  0.0007
     mixed |  white  |0.9875|  0.0059
     white |  white  |0.9897|  0.0038

```{r Visual Search Task Choice Reaction Time, results="show"}

datrt <- summarySEwithin(clean.choice, measurevar ="rt1", withinvars = c("condition","targcol"), idvar = "subid")

rtplot <- ggplot(datrt, aes(x = condition, y=rt1, fill = targcol)) +
  geom_bar(stat = "identity", position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(position=position_dodge(.9), width = .25,
                               aes(ymin=rt1-ci, ymax=rt1+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(1000, 3500)) +
  scale_fill_manual(values=myColors) + ylab("Reaction Time (ms)") +
  ggtitle("Reaction Times of the \n Visual Search Task \n by Condition")
rtplot

vis.ac <- lmer(rt1~condition*targcol*corr+(1|subid),data=clean.choice)
Anova(vis.ac)
```
Reaction time was affected by whether the targets were blocked or mixed (condition), the target color was different, or whether the answer was correct or not. There was also an interaction of condition and correct/incorrect responses.

 condition | target color | reaction time |  ci
 ----------|---------|------|------------
     green |  green  |2694  |  57.76
     mixed |  green  |2689  |  83.87
     mixed |  white  |3180  |  82.75
     white |  white  |3356  |  61.23


### correct drt vs missed drts
```{r}
drt.ac$condition <- recode_factor(drt.ac$condition,"1" = "practice","2" = "green","3" ="white", "4" = "mixed", .default = "NA")

drt.meanhit <- drt.ac %>%
  filter(response != -1) %>%
  dplyr::group_by(subid,condition) %>%
  dplyr::summarise(mean_ac_hits = mean(response)*100) %>% 
  filter(condition != "practice", subid != "03", mean_ac_hits > 50)

drthit <- summarySEwithin(drt.meanhit, measurevar ="mean_ac_hits", withinvars = c("condition"), idvar = "subid")

drt.meanac <- drt.ac %>%
  filter(response != 0) %>%
  mutate(response = ifelse(response == "-1", 0,1)) %>%
  dplyr::group_by(subid,condition) %>%
  dplyr::summarise(mean_ac = mean(response)*100) %>% 
  filter(condition != "practice", subid != "03")

drtac <- summarySEwithin(drt.meanac, measurevar ="mean_ac", withinvars = c("condition"), idvar = "subid")
  
hitplot <- ggplot(drthit, aes(x = condition, y=mean_ac_hits)) +
  geom_bar(stat = "identity",position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(width = .25,
                               aes(ymin=mean_ac_hits-ci, ymax=mean_ac_hits+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(65, 75)) +
  scale_fill_manual(values=myColors) + ylab("Percent Correct (%)") +
  ggtitle("Hits to the \n DRT \n by Condition")
hitplot

drt.hit <- lmer(mean_ac_hits~condition+(1|subid),data=drt.meanhit)
Anova(drt.hit)


acplot <- ggplot(drtac, aes(x = condition, y=mean_ac)) +
  geom_bar(stat = "identity",position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(width = .25,
                               aes(ymin=mean_ac-ci, ymax=mean_ac+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(45, 65)) +
  scale_fill_manual(values=myColors) + ylab("Percent Correct (%)") +
  ggtitle("Accuracy of the \n DRT \n by Condition")
acplot

drt.ac1 <- lmer(mean_ac~condition+(1|subid),data=drt.meanac)
Anova(drt.ac1)

```
Hits to the DRT correctly predicted the steering deviation across the 3 conditions.

### combined steering with drt
```{r choice drt and steering, results="show"}

drt.clean.choice$condition <- recode_factor(drt.clean.choice$condition,"1" = "practice","2" = "green","3" ="white", "4" = "mixed", .default = "NA")
drt.clean.choice$response <- recode_factor(drt.clean.choice$response, "1" = "correct", "-1" = "incorrect", "0" = "miss")

drtrt <- summarySEwithin(drt.clean.choice, measurevar ="rt", withinvars = c("condition","response"), idvar = "subid")

drtrt <- drtrt %>% filter(condition != "practice", response != "miss")

rtplot <- ggplot(drtrt, aes(x = condition, y=rt, fill = response)) +
  geom_bar(stat = "identity", position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(position=position_dodge(.9), width = .25,
                               aes(ymin=rt-ci, ymax=rt+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(600, 750)) + ylab("Reaction Time (ms)") +
  ggtitle("Reaction Times of the \n DRT \n by Condition and Response")
rtplot

drt.rt <- lmer(rt~condition*response*mean.dev+(1|subid),data=drt.clean.choice)
Anova(drt.rt)

```

condition| response |rt      |    ci
 ------|----------|----------|----------
 green |  correct | 685   | 18
 green |incorrect | 657   | 20
 mixed |  correct | 696   | 18
 mixed |incorrect | 670   | 19
 white | correct  | 696   | 16
 white |incorrect | 672   | 18
 

Incorrect responses (where the participant responded to the light more than once) were faster on average than correct responses. The difficulty (condition) also affected reaction times. In addition, there was a difficulty (condition) by response interaction. We can see the effect of difficulty on steering below.

```{r choice drt and steering 2}

drtrt <- summarySEwithin(drt.clean.choice, measurevar ="mean.dev", withinvars = c("condition"), idvar = "subid")

drtrt <- drtrt %>% filter(condition != "practice")

rtplot <- ggplot(drtrt, aes(x = condition, y=mean.dev)) +
  geom_bar(stat = "identity", position = "dodge") + theme_minimal() +
  my.axis.font + geom_errorbar(position=position_dodge(.9), width = .25,
                               aes(ymin=mean.dev-ci, ymax=mean.dev+ci)) +
  xlab("Condition") + coord_cartesian(ylim = c(5, 20)) + ylab("Degrees Deviation") +
  ggtitle("Mean Steering Deviation")
rtplot

drt.rt <- lmer(mean.dev~condition+(1|subid),data=drt.clean.choice)
Anova(drt.rt)
```

condition| mean.dev|ci
---------|---------|-----
green | 16.13 | 0.60
mixed | 11.73 | 0.27
white | 11.46 | 0.22


Alone, the effects of the difficulty of the visual task changed the steering deviation so that (1) at the easiest difficulty, steering was the worst (2) at the highest difficulty, steering was the best, and (3) when participants didn't know whether to expect easy or difficult trials, steering was in between. In this case, participants may have been overloaded for the 3 tasks, and so priority could be given to a task that they thought they could complete. 

```{r results="show"}
clean.choiceac %>%
  group_by(subid, condition) %>%
  dplyr::summarise(trials_completed = n())
```

